Barrier Reef App
================
Download Data
----------
```{r}
setwd("~/Google Drive/Coursera/Data Analysis/Developing data products/reefApp")
download.file("http://era.deedi.qld.gov.au/1776/1/Great_Barrier_Reef_Food_Fish_Stocks.asc","data/fish1.txt",method="curl")
df <- read.csv("data/fish1.csv",header=TRUE)
df <- df[,c(2,3,4,6,8,10)]
```

Clean Data
----------
### Link to fish database

Species data structure:
1. Genus name
2. Species name
3. +/- other

species <- reef$Species word1
genus <- reef$Species word2
link <- http:://www.fishbase.org/summary/Species-genus.html
http://www.fishbase.org/summary/Lethrinus-laticaudis.html

Test strings:
Gymnocranius audleyi (=bitorquatus) # 330
Nemipterus peronii?
Epinephelus rivulatus=summana=ongus # 654
Prob. L. laticaudis (fraenatus) #34 ## Prob. L. = Lethrinus #337
Gymnothorax sp. # 522
Halichoeres sp.? # 670

^[A-Za-z]*[[:space:]][A-Za-z]*
([=][\s][A-Za-z]*$) # capture =...

```{r}
library(stringr)
df$Species <- sub("Prob. L.","Lethrinus",df$Species)
df$Species[337]
df$url <- str_extract(df$Species,"^\\w*\\s\\w*")
df$url[330]
df$url[654]
df$url[337]
df$url[522]
df$url[670]
df$url <- sub(" ","-",df$url)
df$url <- paste("http://www.fishbase.org/summary/",df$url,".html",sep="")
df$url[330]
df$url[654]
df$url[337]
df$url[522]
df$url[670]
write.table(df,file="data/reefData.txt")
```
Present URL
----------
```{r}
df$Details <- paste("<a href=","'",df$url,"'",">",df$Species,"</a>",sep="")
head(df$urls)
write.table(df,file="data/reefData.txt")
```

```{r}
df <- read.table("data/reefData.txt",header=TRUE)
df <- df[,c(1:6,8)]
write.table(df,"data/reefData.txt")
```




Create Graphs
-------------

1. Count by date
2. Count by region
3. Count by reef (slider to filter top 10-101)
4. Species distribution: top 10
```{r}
setwd("~/Google Drive/Coursera/Data Analysis/Developing data products/reefApp")
library(ggplot2)
library(lubridate)
reef <- read.table("data/reefData.txt")
reef$Date <- dmy(reef$Date)
g <- ggplot(reef,aes(Region))
g + geom_bar()
g1 <- ggplot(reef,aes(Reef))
g1 + geom_bar()
g2 <- ggplot(reef,aes(Date))
g2 + geom_bar()
g3 <- ggplot(reef[1:10,],aes(Species))
g3 + geom_bar()
library(ggplot2)
species <- as.data.frame(table(unique(reef)$Species))
colnames(species) <- c("Species","Count")
library(plyr)
species <- arrange(species,desc(Count),Species)
g4 <- ggplot(species[1:30,],aes(Species,Count))
g4+geom_bar()+ theme(axis.text.x = element_text(angle = 90)) + ggtitle("Count Frequency by Species")
```

```{r}
map3 <- Leaflet$new()
map3$setView(c(-18.242835,147.451012), zoom = 13)
map3$marker(c(-17.5228687,146.0301609), bindPopup = "Innisfail")
map3$marker(c(), bindPopup = "Cairns")
map3$marker(c(-19.261112,146.8169144),bindPopup="Townsville")
map3$print("Towns and Cities near the Great Barrier Reef")
```

```{r}
library(maps)
library(mapdata)
map('worldHires',"Australia")
map('worldHires',"Queensland")
points(146.8169144,-19.261112,col=1,pch=19,cex=2)
points(145.7305034,-16.9203249,col=2,pch=19,cex=2)
points(149.1829713,-21.141857,col=3,pch=19,cex=2)
```

